Denotational Semantics of Gradual Typing using Synthetic Guarded Domain Theory

### 2024-01-26 paper-new/discussion.tex
updates mostly to extensional model
update discussion

\subsection{Related Work}
% Discuss Joey Eremondi's thesis on gradual dependent types

@@

\subsection{Benefits and Drawbacks of the Synthetic Approach}

>>>>

\subsection{Related Work}
% Discuss Joey Eremondi's thesis on gradual dependent types
Eremondi \cite{Eremondi_2023} uses guarded type theory to
define a syntactic model for a gradually-typed source
language with dependent types. By working in guarded type theory, they are
able to give an exact semantics to non-terminating computations in a language
which is logically consistent, allowing for metatheoretic results about the
source language to be proven.
%
Similarly to our approach, they define a guarded lift monad to model potentially-
nonterminating computations and use guarded recursion to model the dynamic type.
However, they do not give a denotational semantics to term precision and it is unclear
how to prove the gradual guarantee in this setting.
The work includes a formalization of the syntactic model in Guarded Cubical Agda.

@@

\subsection{Comparison to Explicit Step-Indexing}
